State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
fixed some typos in paper

\caption{Results for connectivity kernel estimate. In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region. \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain. \textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain. \dean{Note: needs to be changed to absolute values if we include it.} \dean{Note: Power and dB needs to be non-italicised.}}

@@

\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations. \dean{Parham: is this true? the distribution of the estimates of $\xi$ show a bias $>0.01$!} The errors fall below $10^{-4}$ after 6 iterations. }

>>>>

\caption{Results for connectivity kernel estimate. In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region. \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain. \textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.}

@@

\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations. The mean difference between errors in consecutive iterations falls below $10^{-4}$ after 6 iterations. }
